---
title:  "Here is a title"
subtitle: "subtitle"
author: "Eli Holmes<br>NOAA Fisheries, NWFSC<br>Seattle, WA"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css", "slides-style.css", "tufte.css"]
    lib_dir: libs
    nature:
      ratio: '4:3'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc( (%current% - 1) / (%total% - 1) * 100%);">
          </div>
        </div>`
---

<!-- This part specs the layout for the slideshow and the footnote that appears on all slides -->

layout: true

.footnote[U.S. Department of Commerce | National Oceanic and Atmospheric Administration | National Marine Fisheries Service]


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

---

## Visualising multiple variables

### Base R

.pull-left-wide[
1. Teach statistical thinking.  
  - Teach statistics as an investigative process of problem-solving and decision making.
  - Give students experience with multivariable thinking [...] to answer challenging questions that require them to investigate and explore relationships among many variables.
1. Focus on conceptual understanding. 
1. Integrate real data with a context and purpose.
1. Foster active learning.
1. **Use technology** to explore concepts and analyse data.
1. Use assessments to improve and evaluate student learning.
]
.pull-right-narrow[
.hand-blue[
NOT use technology that is only applicable in the intro course or that doesn’t follow good science principles
]
]

---

## Visualising multiple variables

### Base R

.pull-left-wide[
1. Teach statistical thinking.  
  - Teach statistics as an investigative process of problem-solving and decision making.
  - Give students experience with multivariable thinking [...] to answer challenging questions that require them to investigate and explore relationships among many variables.
1. Focus on conceptual understanding. 
1. Integrate real data with a context and purpose.
1. Foster active learning.
1. **Use technology** to explore concepts and analyse data.
1. Use assessments to improve and evaluate student learning.
]
.pull-right-narrow[
.hand-blue[
```{r}
plot(1:10)
```
]
]

---

# test


- some content
- a [link](http://www.google.com)


```{r}
r <- 2 + 2
```


.footnote[test a footnote


]

---

.discussion[
- What are other arguments for starting to teach R with the tidyverse?
- Any arguments against it?
]

---

class: middle

# How tidyverse?

---

### .pink[  ]

## ggplot2 $\in$ tidyverse

.pull-left[
- **ggplot2** is tidyverse's data visualization package
- The `gg` in "ggplot2" stands for Grammar of Graphics
- It is inspired by the book **Grammar of Graphics** by Leland Wilkinson
]
.pull-right[
- **ggplot2** is tidyverse's data visualization package
- The `gg` in "ggplot2" stands for Grammar of Graphics
- It is inspired by the book **Grammar of Graphics** by Leland Wilkinson
]