---
title:  "Template"
subtitle: "Basic style without tweaks of the css"
author: "Eli Holmes<br>NOAA Fisheries, NWFSC"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    self_contained: true
    css: ["xaringan-themer.css"]
    lib_dir: libs
    nature:
      ratio: '4:3'
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "Page %current%"
---
layout: true

.footnote[U.S. Department of Commerce | National Oceanic and Atmospheric Administration | National Marine Fisheries Service]

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

---

# Notes

The template and css makes a presentation that has a few tweaks in `slides-style.css`.  `slide-style.css` is adapted from An RStudio workshop on data science [design-ds-classroom](https://github.com/rstudio-conf-2020/design-ds-classroom) by [Mine Cetinkaya-Rundel](https://github.com/mine-cetinkaya-rundel). 

* I have tweaked the title slide css in `slides-style.css` and needed to remove `date:` from the yaml.
* `slides-style.css` has a number of extra customizations such as square for the bullets, some colored boxes, and a wide left column class.
* Instead of page numbers, there is a progress bar across the top.
* You may want to futz with the css for the title at the top of `slides-style.css`


---

## Side margin


.left-column[
The side margin is smaller on the left.

- Figures
- References
- Images

Everything will get scaled to fit.
]
.right-column[
.hand-blue[
```{r fig.height=4}
plot(1:10)
```


]
]

---

# Footnotes

Because the NMFS footnote is already occupying the footnote space, you need to add some linefeeds to move the footnote upward. 




.footnote[It is quite finicky. Add a linefeed and it breaks.<br><br>]


---

# Math

Weirdly it doesn't know `\begin{equation}`. You have to use `$$` bracketing.

$$
\begin{split}
A & = \frac{\pi r^2}{2} \\
 & = \frac{1}{2} \pi r^2
\end{split}
$$

---

class: middle

# A slide with just a title

---

## Two column format

.pull-left[
- **ggplot2** is tidyverse's data visualization package
- The `gg` in "ggplot2" stands for Grammar of Graphics
- It is inspired by the book **Grammar of Graphics** by Leland Wilkinson
]
.pull-right[
- **ggplot2** is tidyverse's data visualization package
- The `gg` in "ggplot2" stands for Grammar of Graphics
- It is inspired by the book **Grammar of Graphics** by Leland Wilkinson
]

---

## Embedded video


You can embed video.

<iframe width="500" height="400" src="https://www.youtube.com/embed/BCMjVc9ncFo" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
]

